\LARGE \bf Enhancing Security in Multi-Robot Systems through Co-Observation Planning, Reachability Analysis, and Network Flow

### 2024-12-12 paper.tex
Finish main paper

\section{Introduction}\label{sec:introduction}
Multi-robot systems (MRS) have found wide applications in various fields. Although offering numerous advantages, the distributed nature and dependence on network communication make the MRS vulnerable to cyber threats, such as unauthorized access, malicious attacks, and data manipulation \cite{brunner2010infiltrating}. This paper addresses a specific scenario in which robots are compromised by \new{physically masquerading} attackers and directed toward \emph{forbidden regions}, which may contain security-sensitive equipment or human workers. {\news A countermeasure to these \emph{plan-deviation attacks} \cite{wardega2019resilience, wardega2023byzantine, wardega2023hola} is to use the onboard sensing capabilities of the robots themselves to perform inter-robot \emph{co-observations} and detect unusual behavior.
These mutual observations establish a \emph{co-observation schedule} alongside the planned path, ensuring that any attempts by a compromised robot to violate safety constraints (such as transgressing into forbidden regions) would break the observation plan and be promptly detected.}

A preliminary version of this approach is presented in \cite{yang2020multi,yang2021multi}. That work extended the grid-world solution from \cite{wardega2019resilience} to continuous configuration spaces, and incorporated the co-observation planning as constraints in \new{the alternating direction method of multipliers (ADMM)-based trajectory optimization solver to accommodate for more flexible objectives. However, such plans are not guaranteed to exist, and the secured trajectory always comes at the cost of overall system performance. As an extension of the previous works \cite{yang2020multi,yang2021multi}, we introduce reachability analysis and network flow to the security problem to find a balance between security and performance.}
In this paper, we incorporate an additional reachability analysis during the planning phase, incorporating constraints based on sets of locations that agents could potentially reach, referred to as \emph{reachability regions}, as a novel perspective to the existing literature. This approach enforces an empty intersection between forbidden regions and the reachability region during trajectory optimization, preventing undetected attacks if an adversary gains control of the robots. We utilize an ellipsoidal boundary to constrain the search space and formulate the ellipsoid as the reachability region constraint. We present a mathematical formulation of the reachability regions \new{as spatio-temporal constraints} compatible with the solver in \cite{yang2020multi}. 
 we also address the feasibility and optimality challenges. For a MRS with unsecured optimal trajectories (without security constraints), we introduce redundant robots and formed them into \emph{sub-teams} with the original ones. These redundant robots are assigned to establish additional co-observations, termed \emph{cross-trajectory co-observations}, within and across different sub-teams. The proposed algorithm focuses on the movement plans for the additional robots, distinct from those dedicated to task objectives, indicating when they should stay with their current sub-team and when they should deviate to join another. This strategy allows sub-teams to preserve the optimal unsecured trajectories (as illustrated in \cref{fig:cross-traj-comparison-set}) without requiring the entire \emph{sub-team} to maintain close proximity to other teams during co-observation events. The cross-trajectory co-observation problem is transformed as a \new{Multi-Agent Pathfinding (MAPF)} problem on roadmap (represented as directed graph) and solved as a network flow problem \cite{yu2013multi}.

\begin{figure}
	\centering
    \subfloat[Plan-deviation attack\label{fig:example-plan-dev}]{\includegraphics[width = 0.32\linewidth]{plan-deviation}}
    \subfloat[Co-observation \label{fig:example-co-observation}]{\includegraphics[width=0.32\linewidth]{co-observ}}
    \subfloat[Cross-trajectory co-observation \label{fig:example-cross-traj}]{\includegraphics[width=0.32\linewidth]{cross-traj}}

@@

The update steps of the algorithm are then derived as \cite{Boyd2011}:
\begin{subequations}\label{eq:ADMMupdate}
	\begin{align}
		\vq^{k+1}&:=\argmin_\vq(\varPhi(\vq^k) +\frac{\rho}{2}\norm{D(\vq)-\vz^k+\vu^k}_2^2),\label{eq:admm-mod-update-q}\\
		\vz^{k+1}&:=\Pi_\mathcal{Z}(D(\vq^{k+1})+\vu^k), \label{eq:z-update} \\
		\vu^{k+1}&:=\vu^k+D(\vq^{k+1})-\vz^{k+1}, \label{eq:u-update}
	\end{align}
\end{subequations}
where $\Pi_\mathcal{Z}$ is the new projection function to the modified constraint set $\mathcal{Z}$, $\vu$ represents a scaled dual variable that, intuitively, accumulates the sum of primal residuals
\begin{equation}\label{eq:primal-residual}
	\vr^{k}=D(\vq^{k+1})-\vz^{k+1}.
\end{equation}
Checking the primal residuals alongside the dual residuals 
\begin{equation}\label{eq:dual-residual}
	\vs^{k}=-\rho(\vz^{k}-\vz^{k-1})
\end{equation}
after each iteration, the steps are reiterated until convergence when the primal and dual residuals are small, or divergence when primal and dual residuals remain large after a fixed number of iterations.
{\news
\begin{remark}
In practical application, \eqref{eq:admm-mod-update-q} is solved iteratively via a nonlinear optimization solver such as \emph{fmincon} \rtron{Add ref}. The use of explicit gradients of the constraint functions (derived below) greatly enhances the solver's efficiency and accuracy (with respect to the use of numericall differentiation). At the same time, \eqref{eq:z-update} and~\eqref{eq:u-update} have closed form solutions.
\end{remark}
}
% \rtron{Maybe state here that (9a) is solved iteratively, while (9b) and (9c) are closed-form.}

@@

For simplicity, in this paper we consider only a maximum velocity constraint $v_{max}$; the reachability region for $q'$ can then be over-approximated by the following (the over-approximation is obtained by neglecting physical obstacles):%$\mathcal{E}=\{q'\in\mathbb{R}^n: d(q_1,q')+d(q'q_2)<v_{max}(t_2-t_1)\}$, where $d(\cdot,\cdot)$ denotes the Euclidean distance between two points.
\begin{definition}\label{def:Reachability}
	The \emph{reachability ellipsoid $\cE$} is defined as the region $\mathcal{E}(q_1,q_2,t_{1},t_{2})=\{\tilde{q}\in\mathbb{R}^n: d(q_1,\tilde{q})+d(\tilde{q},q_2)<2a\}$, where $a=\frac{v_{max}}{2}(t_2-t_1)$, and $d(\cdot,\cdot)$ denotes the Euclidean distance between two points.
\end{definition}
This region is an ellipsoid because it represents the set of points $q'$ whose sum of distances two \emph{foci} $q_1$ and $q_2$ is less than $2a$, where a is the major radius of the ellipsoid. }
 \begin{figure}
    \centering
    \subfloat[Showcase of a reachability region\label{fig:EllipseConstraintExample}]{\includegraphics[width=0.47\linewidth, trim = 2cm 2.5cm 2cm 5cm]{Reachability}}
    \subfloat[Point-ellipsoid constraint \label{fig:Ellipse-to-point}]{\includegraphics[width=0.47\linewidth, trim = 0.3cm 1.3cm 0.3cm 1.3cm, clip]{Ellipse2point}}

    \subfloat[Plane-ellipse constraint \label{fig:Ellipse-to-plane}]{ \includegraphics[width=0.47\linewidth, trim = 0.3cm 1cm 0.3cm 1cm, clip]{Ellipse2line_V2}}
    \subfloat[Polygon-ellipse constraint \label{fig:Ellipse-to-safezone}]{\includegraphics[width=0.47\linewidth,trim = 0cm 1cm 0.3cm 0.5cm, clip]{Ellipse2safezone_V2}}

@@

%Based on the schedule, reachability for agent 1 in-between the scheduled co-observations are constrained. Notice that additional checkpoint (i.e. stationary security camera) need to be incorporated in order to generated an attack-proof solution. Additional solutions to avoid these checkpoints will be discussed in \cref{sec:cross-trajectory}.  
%The result of the simulation is shown in Fig.~\ref{fig:ReachabilitySimulation}. The reachability regions are shown as black ellipsoids, and we can show that all of them have empty intersections with Zone 2 and 3. Notice that no explicit constraints have been enabled between reachability regions and obstacles, because we assume that robots have the basic obstacle avoidance capability and can not go through any hard obstacles. Therefore, the intersections between obstacles and ellipsoids, i.e. the case here between agent 3 and zone 1, are tolerable. All constraints have been satisfied and, to the best of their capability, agents have spread out across the map to perform the best possible exploration task. 
\begin{figure}
  \centering
  % \subfloat[Grid-world trajectory. \label{fig:Grid-example-application}]{\includegraphics[width=0.45\linewidth, trim = 2cm 0.5cm 0cm 2cm]{Kacper_result}}
  \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[height = 0.47\linewidth,trim =0cm 0cm 0cm 0cm, clip,valign=t]{Grid_world}}
  % \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth,valign=c]{SecurityBreak_v2}}
  \subfloat[Secured result \label{fig:ReachabilitySimulation}]{\includegraphics[height=0.47\linewidth,trim =2cm 1.8cm 2cm 1.5cm, clip,valign=t]{FinalResult}}
  \caption{{\news Trajectory design a three-robot system based on the grid world result. Zone 1 is an obstacle, Zone 2 and Zone 3 are forbidden regions. (\ref{fig:Grid-example-application}) Result of the APMAPF algorithm in $8\times8$ grid-world without the map exploring objective. (\ref{fig:ReachabilitySimulation}) The secured trajectory with the incorporation of co-observation generated by APMAPF and additional reachability constraints.}}
  \label{fig:example-application}
\end{figure}

@@

In this section, we define and search for security checkpoints and how to use \rrtstar{} to construct the checkpoint graph $G_{q}$.
A heuristic approach is provided to locate the checkpoints on given trajectories (an optimal solution would likely be NP-hard, while the approach below works well enough for our purpose). %with a toy example shown in Figure \ref{fig:checkpoint-generate}.

{\news \rtron{Use enumerate} We begin by adding the start and end locations $(q_{p}(t_0),t_0)$, $(q_{p}(t_2),t_2)$ to $V_{p}$, with $t_{0}=0$, $t_2=T$ as \emph{start} and \emph{end verticies}. Then, we search for the largest $t_{1} \in \{t_{0}+1, \dots ,t_{2}\}$ such that the reachability ellipsoid between $q_{p}(t_{0})$ and $q_{p}(t_{1})$ has no overlap with any of the forbidden areas, i.e. $\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{1}), t_{0},t_{1})\intersect F = \emptyset$. Then $(q_{p}(t_{1}),t_1)$ is added to $V_{p}$. Simultaneously, we search backward to find $q_{p}(t_{3})$ with the smallest $t_{3}\in \{t_{1},\dots,t_{2}-1\} $ that meets the reachability requirement $\mathcal{E}(q_{p}(t_{2}),q_{p}(t_{3}),t_{2},t_{3}) \intersect F = \emptyset$. Then $(q_{p}(t_{3}),t_3)$ is added to $V_{p}$. Finally, we set $t_{0}\leftarrow t_{1}$, $t_{2}\leftarrow t_{3}$ and repeat the same process. The search is stopped when $\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{2}),t_{0},t_{2}) \intersect F = \emptyset$ or $t_{0}>t_{2}$. A toy example is shown in \cref{fig:checkpoint-generate}. }

\begin{figure}
	\centering
    \subfloat[]{\includegraphics[width=0.45\linewidth,trim = 1.7cm 2cm 1cm 2.7cm, clip,valign=c]{SC_gen_1}}
    \subfloat[]{\includegraphics[width=0.45\linewidth,trim = 1.7cm 2cm 1cm 2.7cm, clip,valign=c]{SC_gen_2}}
    \caption{\news{Checkpoint generation example}}\label{fig:checkpoint-generate}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
  \subfloat[Cross-trajectory edge generation\label{fig:two-edges}]{\includegraphics[width=0.45\linewidth,trim = 0cm 0cm 0cm 0cm, clip, valign=c]{two_edges}}
  \subfloat[Full checkpoint graph\label{fig:security-graph-generate}]{\includegraphics[width=0.45\linewidth,trim = 0cm 0cm 0cm 0.2cm, clip, valign=c]{security_graph}}
  \caption{{\news (\ref{fig:two-edges}) The latest departure node $q^{d}_{b}$ found for $v_{r1}$ and the earliest arrival node $q^{a}_{b}$ found for $v_{r3}$. (\ref{fig:security-graph-generate}) A full checkpoint graph, where circles are checkpoints $V_p$, triangles are connection nodes $V_c$, colored arrows (red and blue) are trajectory edges $E_t$ and black arrows are cross-trajectory edges $E_c$.}}  
\end{figure}

>>>>

\section{Introduction}\label{sec:introduction}
Multi-robot systems (MRS) have found wide applications in various fields. \new{Although offering numerous advantages, the distributed nature and dependence on network communication make the MRS vulnerable to cyber threats, such as unauthorized access, malicious attacks, and data manipulation \cite{brunner2010infiltrating}.} This paper addresses a specific scenario in which robots are compromised by \new{physically masquerading} attackers and directed toward \emph{forbidden regions}, which may contain security-sensitive equipment or human workers. {\news A countermeasure to these \emph{plan-deviation attacks} \cite{wardega2019resilience, wardega2023byzantine, wardega2023hola} is to use the onboard sensing capabilities of the robots themselves to perform inter-robot \emph{co-observations} and detect unusual behavior.
These mutual observations establish a \emph{co-observation schedule} alongside the planned path, ensuring that any attempts by a compromised robot to violate safety constraints (such as transgressing into forbidden regions) would break the observation plan and be promptly detected.}

A preliminary version of this approach is presented in \cite{yang2020multi,yang2021multi}. That work extended the grid-world solution from \cite{wardega2019resilience} to continuous configuration spaces, and incorporated the co-observation planning as constraints in \new{the alternating direction method of multipliers (ADMM)-based trajectory optimization solver to accommodate for more flexible objectives. However, such plans are not guaranteed to exist, and the secured trajectory always comes at the cost of overall system performance. As an extension of the previous works \cite{yang2020multi,yang2021multi}, we introduce reachability analysis and network flow to the security problem to find a balance between security and performance.}

In this paper, we incorporate additional reachability analysis during the planning phase, incorporating constraints based on sets of locations that agents could potentially reach, referred to as \emph{reachability regions}, as a novel perspective to the existing literature. This approach enforces an empty intersection between forbidden regions and the reachability region during trajectory optimization, preventing undetected attacks if an adversary gains control of the robots. We utilize an ellipsoidal boundary to constrain the search space and formulate the ellipsoid as the reachability region constraint. We present a mathematical formulation of the reachability regions \new{as spatio-temporal constraints} compatible with the solver in \cite{yang2020multi}.

\new{Furthermore, we address the feasibility and optimality challenges. For a MRS with unsecured optimal trajectories (without security constraints), we introduce redundant robots and formed them into \emph{sub-teams} with the original ones.} These redundant robots are assigned to establish additional co-observations, termed \emph{cross-trajectory co-observations}, within and across different sub-teams. The proposed algorithm focuses on the movement plans for the additional robots, distinct from those dedicated to task objectives, indicating when they should stay with their current sub-team and when they should deviate to join another. This strategy allows sub-teams to preserve the optimal unsecured trajectories (as illustrated in \cref{fig:cross-traj-comparison-set}) without requiring the entire \emph{sub-team} to maintain close proximity to other teams during co-observation events. The cross-trajectory co-observation problem is transformed as a \new{Multi-Agent Pathfinding (MAPF)} problem on roadmap (represented as directed graph) and solved as a network flow problem \cite{yu2013multi}.

\begin{figure}
	\centering
    \subfloat[Plan-deviation attack\label{fig:example-plan-dev}]{\includegraphics[width = 0.32\linewidth]{plan-deviation-v2}}
    \subfloat[Co-observation \label{fig:example-co-observation}]{\includegraphics[width=0.32\linewidth]{co-observ-v2}}
    \subfloat[Cross-trajectory co-observation \label{fig:example-cross-traj}]{\includegraphics[width=0.32\linewidth]{cross-traj-v2}}

@@

The update steps of the algorithm are then derived as \cite{Boyd2011}:
\begin{subequations}\label{eq:ADMMupdate}
	\begin{align}
		\vq^{k+1}&:=\argmin_\vq(\varPhi(\vq^k) +\frac{\rho}{2}\norm{D(\vq)-\vz^k+\vu^k}_2^2),\label{eq:admm-mod-update-q}\\
		\vz^{k+1}&:=\Pi_\mathcal{Z}(D(\vq^{k+1})+\vu^k), \label{eq:z-update} \\
		\vu^{k+1}&:=\vu^k+D(\vq^{k+1})-\vz^{k+1}, \label{eq:u-update}
	\end{align}
\end{subequations}
where $\Pi_\mathcal{Z}$ is the new projection function to the modified constraint set $\mathcal{Z}$, $\vu$ represents a scaled dual variable that, intuitively, accumulates the sum of primal residuals
\begin{equation}\label{eq:primal-residual}
	\vr^{k}=D(\vq^{k+1})-\vz^{k+1}.
\end{equation}
Checking the primal residuals alongside the dual residuals 
\begin{equation}\label{eq:dual-residual}
	\vs^{k}=-\rho(\vz^{k}-\vz^{k-1})
\end{equation}
after each iteration, the steps are reiterated until convergence when the primal and dual residuals are small, or divergence when primal and dual residuals remain large after a fixed number of iterations.
{\news
\begin{remark}
In practical application, \eqref{eq:admm-mod-update-q} is solved iteratively via a nonlinear optimization solver such as \emph{fmincon}~\cite{MATLAB:fmincon}. The use of explicit gradients of the constraint functions (derived below) greatly enhances the solver's efficiency and accuracy (with respect to the use of numericall differentiation). At the same time, \eqref{eq:z-update} and~\eqref{eq:u-update} have closed form solutions.
\end{remark}
}
% \rtron{Maybe state here that (9a) is solved iteratively, while (9b) and (9c) are closed-form.}

@@

For simplicity, in this paper we consider only a maximum velocity constraint $v_{max}$; the reachability region for $q'$ can then be over-approximated by the following (the over-approximation is obtained by neglecting physical obstacles):%$\mathcal{E}=\{q'\in\mathbb{R}^n: d(q_1,q')+d(q'q_2)<v_{max}(t_2-t_1)\}$, where $d(\cdot,\cdot)$ denotes the Euclidean distance between two points.
\begin{definition}\label{def:Reachability}
	The \emph{reachability ellipsoid $\cE$} is defined as the region $\mathcal{E}(q_1,q_2,t_{1},t_{2})=\{\tilde{q}\in\mathbb{R}^n: d(q_1,\tilde{q})+d(\tilde{q},q_2)<2a\}$, where $a=\frac{v_{max}}{2}(t_2-t_1)$, and $d(\cdot,\cdot)$ denotes the Euclidean distance between two points.
\end{definition}
This region is an ellipsoid because it represents the set of points $q'$ whose sum of distances two \emph{foci} $q_1$ and $q_2$ is less than $2a$, where a is the major radius of the ellipsoid. }
 \begin{figure}
    \centering
    \subfloat[Showcase of a reachability region\label{fig:EllipseConstraintExample}]{\includegraphics[width=0.47\linewidth]{Reachability-v2}}
    \subfloat[Point-ellipsoid constraint \label{fig:Ellipse-to-point}]{\includegraphics[width=0.47\linewidth]{Ellipse2point-v2}}

    \subfloat[Plane-ellipse constraint \label{fig:Ellipse-to-plane}]{ \includegraphics[width=0.47\linewidth]{Ellipse2line-v3}}
    \subfloat[Polygon-ellipse constraint \label{fig:Ellipse-to-safezone}]{\includegraphics[width=0.47\linewidth]{Ellipse2safezone-v3}}

@@

%Based on the schedule, reachability for agent 1 in-between the scheduled co-observations are constrained. Notice that additional checkpoint (i.e. stationary security camera) need to be incorporated in order to generated an attack-proof solution. Additional solutions to avoid these checkpoints will be discussed in \cref{sec:cross-trajectory}.  
%The result of the simulation is shown in Fig.~\ref{fig:ReachabilitySimulation}. The reachability regions are shown as black ellipsoids, and we can show that all of them have empty intersections with Zone 2 and 3. Notice that no explicit constraints have been enabled between reachability regions and obstacles, because we assume that robots have the basic obstacle avoidance capability and can not go through any hard obstacles. Therefore, the intersections between obstacles and ellipsoids, i.e. the case here between agent 3 and zone 1, are tolerable. All constraints have been satisfied and, to the best of their capability, agents have spread out across the map to perform the best possible exploration task. 
\begin{figure}
  \centering
  % \subfloat[Grid-world trajectory. \label{fig:Grid-example-application}]{\includegraphics[width=0.45\linewidth, trim = 2cm 0.5cm 0cm 2cm]{Kacper_result}}
  \subfloat[\new{Grid world result.}\label{fig:Grid-example-application}]{\includegraphics[height = 0.47\linewidth,trim =0cm 0cm 0cm 0cm, clip,valign=t]{Grid_world}}
  % \subfloat[Continuous world trajectory \label{fig:SecurityBreak}]{\includegraphics[width=0.45\linewidth,valign=c]{SecurityBreak_v2}}
  \subfloat[Secured result \label{fig:ReachabilitySimulation}]{\includegraphics[height=0.47\linewidth,valign=t]{FinalResult-v2}}
  \caption{{\news Trajectory design a three-robot system based on the grid world result. Zone 1 is an obstacle, Zone 2 and Zone 3 are forbidden regions. (\ref{fig:Grid-example-application}) Result of the APMAPF algorithm in $8\times8$ grid-world without the map exploring objective. (\ref{fig:ReachabilitySimulation}) The secured trajectory with the incorporation of co-observation generated by APMAPF and additional reachability constraints. Attack attempts into forbidden region (red dashed line) will cause team 1 miss next scheduled co-observation.}}
  \label{fig:example-application}
\end{figure}

@@

In this section, we define and search for security checkpoints and how to use \rrtstar{} to construct the checkpoint graph $G_{q}$.
{\news We use a heuristic approach (~\cref{alg:graph}) to locate the checkpoints on given trajectories. \cref{alg:graph} is applied independently to each sub-team to generate their initial checkpoints.” While an optimal solution would likely be NP-hard, this approach works well enough for our purpose.} %with a toy example shown in Figure \ref{fig:checkpoint-generate}.

% {\news
%   \begin{enumerate}
%   \item Initialization: Add the start and end locations $(q_{p}(t_0),t_0)$, $(q_{p}(t_2),t_2)$ to $V_{p}$, where $t_{0}=0$, $t_2=T$ as \emph{start} and \emph{end verticies}.
%   \item Forward search: Find the largest $t_{1} \in \{t_{0}+1, \dots ,t_{2}\}$ such that the reachability ellipsoid $\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{1}), t_{0},t_{1})$ does not overlap with any of the forbidden areas $F$. Once found, add $(q_{p}(t_{1}),t_1)$ to $V_{p}$.
%   \item Backward search: Find the smallest $t_{3}\in \{t_{1},\dots,t_{2}-1\}$ such that the reachability ellipsoid $\mathcal{E}(q_{p}(t_{2}),q_{p}(t_{3}),t_{2},t_{3})$ does not overlap with any of the forbidden areas $F$. Once found, add $(q_{p}(t_{3}),t_3)$ to $V_{p}$.
%   \item Update indices: $t_{0}\leftarrow t_{1}$, $t_{2}\leftarrow t_{3}$.
%   \item Repeat the process until: $\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{2}),t_{0},t_{2}) \intersect F = \emptyset$ or $t_{0}>t_{2}$
% \end{enumerate}}

  \begin{algorithm}\label{alg:graph}
  \caption{Checkpoint Graph Initialization for Team $\cI_p$}
  {\news \begin{algorithmic}[1]
  \State \textbf{Initialization:} Add $(q_{p}(t_0),t_0)$ and $(q_{p}(t_2),t_2)$ to $V_{p}$, where $t_{0} = 0$ and $t_{2} = T$, as \emph{start} and \emph{end vertices}.
  \While{$\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{2}),t_{0},t_{2}) \cap F \neq \emptyset$ \textbf{and} $t_{0} \leq t_{2}$}
      \State \textbf{Forward Search:} Find the largest $t_{1} \in \{t_{0}+1, \dots, t_{2}\}$ such that $\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{1}), t_{0},t_{1}) \cap F = \emptyset$. Then add $(q_{p}(t_{1}),t_{1})$ to $V_{p}$.
      \State \textbf{Backward Search:} Find the smallest $t_{3}\in\{t_{1}, \dots, t_{2}-1\}$ such that $
      \mathcal{E}(q_{p}(t_{2}),q_{p}(t_{3}), t_{2},t_{3}) \cap F = \emptyset.$ Then add $(q_{p}(t_{3}),t_{3})$ to $V_{p}$.
      \State \textbf{Update Indices:} Set $t_{0} \leftarrow t_{1}$ and $t_{2} \leftarrow t_{3}$.
  \EndWhile
  \end{algorithmic}}
  \end{algorithm}
% {\news We begin by adding the start and end locations $(q_{p}(t_0),t_0)$, $(q_{p}(t_2),t_2)$ to $V_{p}$, with $t_{0}=0$, $t_2=T$ as \emph{start} and \emph{end verticies}. Then, we search for the largest $t_{1} \in \{t_{0}+1, \dots ,t_{2}\}$ such that the reachability ellipsoid between $q_{p}(t_{0})$ and $q_{p}(t_{1})$ has no overlap with any of the forbidden areas, i.e. $\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{1}), t_{0},t_{1})\intersect F = \emptyset$. Then $(q_{p}(t_{1}),t_1)$ is added to $V_{p}$. Simultaneously, we search backward to find $q_{p}(t_{3})$ with the smallest $t_{3}\in \{t_{1},\dots,t_{2}-1\} $ that meets the reachability requirement $\mathcal{E}(q_{p}(t_{2}),q_{p}(t_{3}),t_{2},t_{3}) \intersect F = \emptyset$. Then $(q_{p}(t_{3}),t_3)$ is added to $V_{p}$. Finally, we set $t_{0}\leftarrow t_{1}$, $t_{2}\leftarrow t_{3}$ and repeat the same process. The search is stopped when $\mathcal{E}(q_{p}(t_{0}),q_{p}(t_{2}),t_{0},t_{2}) \intersect F = \emptyset$ or $t_{0}>t_{2}$. A toy example is shown in \cref{fig:checkpoint-generate}. }

\begin{figure}
	\centering
    \subfloat[]{\includegraphics[width=0.45\linewidth,valign=c]{SC_gen_1-v2}}
    \subfloat[]{\includegraphics[width=0.45\linewidth,valign=c]{SC_gen_2-v2}}
    \caption{\news{Checkpoint generation example}}\label{fig:checkpoint-generate}
\end{figure}

@@

\begin{figure}[htbp]
    \centering
  \subfloat[Cross-trajectory edge generation\label{fig:two-edges}]{\includegraphics[width=0.45\linewidth,valign=c]{two_edges-v2}}
  \subfloat[Full checkpoint graph\label{fig:security-graph-generate}]{\includegraphics[width=0.45\linewidth,valign=c]{security_graph-v2}}
  \caption{{\news (\ref{fig:two-edges}) The latest departure node $q^{d}_{b}$ found for $v_{r1}$ and the earliest arrival node $q^{a}_{b}$ found for $v_{r3}$. (\ref{fig:security-graph-generate}) A full checkpoint graph, where circles are checkpoints $V_p$, triangles are connection nodes $V_c$, colored arrows (red and blue) are trajectory edges $E_t$ and black arrows are cross-trajectory edges $E_c$.}}  
\end{figure}
